---
title: "Social_Networks_Project"
author: "Natalie Samuels"
date created: "9/5/2018"
last edited: "9/29/2018"
output: html_document
---

Read in combined dd_trait csv
```{r}
dd_trait_data = read.csv(file='dd_trait_nsamuels.csv')
```


Create dummy variables for event categories
```{r}
# change category variables from numeric to named factors
dd_trait_data$Category[dd_trait_data$Category == 1] = 'Soc_Rel'
dd_trait_data$Category[dd_trait_data$Category == 2] = 'School'
dd_trait_data$Category[dd_trait_data$Category == 3] = 'Health'
dd_trait_data$Category[dd_trait_data$Category == 4] = 'Fin'
dd_trait_data$Category[dd_trait_data$Category == 5] = 'Job'
dd_trait_data$Category[dd_trait_data$Category == 6] = 'Other'
dd_trait_data$Category = as.factor(dd_trait_data$Category)

# create dummy variables for event categories (indicator == School)
dd_trait_data$Cat_Soc_Rel = ifelse(dd_trait_data$Category == 'Soc_Rel', 1, 0)
dd_trait_data$Cat_Health = ifelse(dd_trait_data$Category == 'Health', 1, 0)
dd_trait_data$Cat_Fin = ifelse(dd_trait_data$Category == 'Fin', 1, 0)
dd_trait_data$Cat_Job = ifelse(dd_trait_data$Category == 'Job', 1, 0)
dd_trait_data$Cat_Other = ifelse(dd_trait_data$Category == 'Other', 1, 0)
```


Create effect column for event valence
```{r}
dd_trait_data$Val_EC = ifelse(dd_trait_data$Valence == 'Pos', 1, -1)
```


Mean-center EmoRating, STAI_MEAN, CESD_avg, Loneliness_avg, and PSS_avg
```{r}
mean_center = function(column)
{
  scale(column, scale=FALSE)
}

dd_trait_data$STAI_MEAN_ctr = mean_center(dd_trait_data$STAI_MEAN)

dd_trait_data$CESD_avg_ctr = mean_center(dd_trait_data$CESD_avg)

dd_trait_data$Loneliness_avg_ctr = mean_center(dd_trait_data$Loneliness_avg)

dd_trait_data$PSS_avg_ctr = mean_center(dd_trait_data$PSS_avg)

# emotion rating for negative events, person-centered
dd_trait_data$EmoRating_neg_pctr[dd_trait_data$Val_EC==-1] = dd_trait_data$EmoRating[dd_trait_data$Val_EC==-1] - ave(dd_trait_data$EmoRating[dd_trait_data$Val_EC==-1], dd_trait_data$ID[dd_trait_data$Val_EC==-1], FUN=function(x) mean(x, na.rm=TRUE))

```


Regression analysis for event qualities (EmoRating & Cat), predicting whether student seeks help.

Original model:
ev_qual_got_help_model = glmer(GotHelp ~ EmoRating_neg_pctr*Cat_Soc_Rel + EmoRating_neg_pctr*Cat_Health + EmoRating_neg_pctr*Cat_Fin + EmoRating_neg_pctr*Cat_Job + EmoRating_neg_pctr*Cat_Other + (1 | ID/Dorm) + (0 + EmoRating_neg_pctr | ID/Dorm) + (0 + Cat_Soc_Rel | ID/Dorm) + (0 + EmoRating_neg_pctr:Cat_Soc_Rel | ID/Dorm) + (0 + Cat_Health | ID/Dorm) + (0 + EmoRating_neg_pctr:Cat_Health | ID/Dorm) +  (0 + Cat_Fin | ID/Dorm) + (0 + EmoRating_neg_pctr:Cat_Fin | ID/Dorm) + (0 + Cat_Job | ID/Dorm) + (0 + EmoRating_neg_pctr:Cat_Job | ID/Dorm) +  (0 + Cat_Other | ID/Dorm) + (0 + EmoRating_neg_pctr:Cat_Other | ID/Dorm), data=subset(dd_trait_data, (Val_EC==-1)), family=binomial, control=glmerControl(optimizer='bobyqa'))

```{r}
library(lme4)
ev_qual_got_help_model = glmer(GotHelp ~ EmoRating_neg_pctr*Cat_Soc_Rel + EmoRating_neg_pctr*Cat_Health + EmoRating_neg_pctr*Cat_Fin + EmoRating_neg_pctr*Cat_Job + EmoRating_neg_pctr*Cat_Other + (0 + EmoRating_neg_pctr:Cat_Fin | ID), data=subset(dd_trait_data, (Val_EC==-1)), family=binomial, control=glmerControl(optimizer='bobyqa'))

```


Regression analysis for trait anxiety and EmoRating, predicting whether student seeks help.

Original model:
anxiety_got_help_model = glmer(GotHelp ~ EmoRating_neg_pctr*STAI_MEAN_ctr + (1 | ID/Dorm) + (0 + EmoRating_neg_pctr | ID/Dorm) + (0 + STAI_MEAN_ctr | ID/Dorm) + (0 + EmoRating_neg_pctr:STAI_MEAN_ctr | ID/Dorm), data=subset(dd_trait_data, (Val_EC==-1)), family=binomial, control=glmerControl(optimizer='bobyqa'))

```{r}
anxiety_got_help_model = glmer(GotHelp ~ EmoRating_neg_pctr*STAI_MEAN_ctr + (1 | Dorm) + (0 + EmoRating_neg_pctr | ID/Dorm) + (0 + STAI_MEAN_ctr | ID), data=subset(dd_trait_data, (Val_EC==-1)), family=binomial, control=glmerControl(optimizer='bobyqa'))

```


Regression analysis for trait depression and EmoRating, predicting whether student seeks help.

Original model:
depression_got_help_model = glmer(GotHelp ~ EmoRating_neg_pctr*CESD_avg_ctr + (1 | ID/Dorm) + (0 + EmoRating_neg_pctr | ID/Dorm) + (0 + CESD_avg_ctr | ID/Dorm) + (0 + EmoRating_neg_pctr:CESD_avg_ctr | ID/Dorm), data=subset(dd_trait_data, (Val_EC==-1)), family=binomial, control=glmerControl(optimizer='bobyqa'))

```{r}
depression_got_help_model = glmer(GotHelp ~ EmoRating_neg_pctr*CESD_avg_ctr + (1 | ID/Dorm) + (0 + EmoRating_neg_pctr | ID/Dorm), data=subset(dd_trait_data, (Val_EC==-1)), family=binomial, control=glmerControl(optimizer='bobyqa'))

```


Regression analysis for trait lonliness and EmoRating, predicting whether student seeks help.

Original model:
lonliness_got_help_model = glmer(GotHelp ~ EmoRating_neg_pctr*Loneliness_avg_ctr + (1 | ID/Dorm) + (0 + EmoRating_neg_pctr | ID/Dorm) + (0 + Loneliness_avg_ctr | ID/Dorm) + (0 + EmoRating_neg_pctr:Loneliness_avg_ctr | ID/Dorm), data=subset(dd_trait_data, (Val_EC==-1)), family=binomial, control=glmerControl(optimizer='bobyqa'))

```{r}
lonliness_got_help_model = glmer(GotHelp ~ EmoRating_neg_pctr*Loneliness_avg_ctr + (1 | ID/Dorm) + (0 + Loneliness_avg_ctr | ID/Dorm) + (0 + EmoRating_neg_pctr:Loneliness_avg_ctr | ID/Dorm), data=subset(dd_trait_data, (Val_EC==-1)), family=binomial, control=glmerControl(optimizer='bobyqa'))

```


Regression analysis for perceived stress and EmoRating, predicting whether student seeks help.

Original model:
stress_got_help_model = glmer(GotHelp ~ EmoRating_neg_pctr*PSS_avg_ctr + (1 | ID/Dorm) + (0 + EmoRating_neg_pctr | ID/Dorm) + (0 + PSS_avg_ctr | ID/Dorm) + (0 + EmoRating_neg_pctr:PSS_avg_ctr | ID/Dorm), data=subset(dd_trait_data, (Val_EC==-1)), family=binomial, control=glmerControl(optimizer='bobyqa'))

```{r}
stress_got_help_model = glmer(GotHelp ~ EmoRating_neg_pctr*PSS_avg_ctr + (1 | ID), data=subset(dd_trait_data, (Val_EC==-1)), family=binomial, control=glmerControl(optimizer='bobyqa'))

```


TAKEAWAYS 9/24:
1) lonliness and event category matter for whether people disclose NegEv
  a) lonliness correlated with depression, anxiety (although neither depression nor anxiety predicts GotHelp)
  Categories: Social Relationships*** (-), Health** (-), Job* (-), Other*** (-)
  Lonliness** (-)
2) emotion rating matters somewhat for whether people disclose NegEv
  a) how to report?


NEXT STEPS:
1) Figure out how to predict continuous DV (linear regression?) for NumDrmTld
  a) test TOIs on NumDrmTld
2) What's the emotion rating associated with each event category?
3) **Do students high in lonliness feel better after disclosing events?
  b) Compared to students who feel less lonlely?
  c) **How do lonely students fare at the end of the quarter?

