---
title: "Social_Networks_Project"
author: "Natalie Samuels"
date created: "9/5/2018"
last edited: "10/24/2018"
output: html_document
---
# Trait and situational predictors of self-disclosure in college freshmen.

```{r echo=FALSE}
# Read in combined dd_trait csv
dd_trait_data = read.csv(file='dd_trait_nsamuels.csv')
```


```{r echo=FALSE}
# Create dummy variables for event categories

# change category variables from numeric to named factors
dd_trait_data$Category[dd_trait_data$Category == 1] = 'Soc_Rel'
dd_trait_data$Category[dd_trait_data$Category == 2] = 'School'
dd_trait_data$Category[dd_trait_data$Category == 3] = 'Health'
dd_trait_data$Category[dd_trait_data$Category == 4] = 'Fin'
dd_trait_data$Category[dd_trait_data$Category == 5] = 'Job'
dd_trait_data$Category[dd_trait_data$Category == 6] = 'Other'
dd_trait_data$Category = as.factor(dd_trait_data$Category)

# create dummy variables for event categories (indicator == School)
dd_trait_data$Cat_Soc_Rel = ifelse(dd_trait_data$Category == 'Soc_Rel', 1, 0)
dd_trait_data$Cat_Health = ifelse(dd_trait_data$Category == 'Health', 1, 0)
dd_trait_data$Cat_Fin = ifelse(dd_trait_data$Category == 'Fin', 1, 0)
dd_trait_data$Cat_Job = ifelse(dd_trait_data$Category == 'Job', 1, 0)
dd_trait_data$Cat_Other = ifelse(dd_trait_data$Category == 'Other', 1, 0)
```


```{r echo=FALSE}
# Create effect column for event valence
dd_trait_data$Val_EC = ifelse(dd_trait_data$Valence == 'Pos', 1, -1)
```


```{r echo=FALSE}
# Mean-center EmoRating, STAI_MEAN, CESD_avg, Loneliness_avg, PSS_avg, and CloseFrd_Total
mean_center = function(column)
{
  scale(column, scale=FALSE)
}

dd_trait_data$STAI_MEAN_ctr = mean_center(dd_trait_data$STAI_MEAN)

dd_trait_data$CESD_avg_ctr = mean_center(dd_trait_data$CESD_avg)

dd_trait_data$Loneliness_avg_ctr = mean_center(dd_trait_data$Loneliness_avg)

dd_trait_data$PSS_avg_ctr = mean_center(dd_trait_data$PSS_avg)

dd_trait_data$CloseFrd_Total_ctr = mean_center(dd_trait_data$CloseFrd_Total)

# emotion rating for negative events, person-z-scored
dd_trait_data$EmoRating_neg_pz[dd_trait_data$Val_EC == -1] = ave(dd_trait_data$EmoRating[dd_trait_data$Val_EC==-1], dd_trait_data$ID[dd_trait_data$Val_EC == -1], FUN=function(x) scale(x))

```


```{r echo=FALSE}
# subsetting dd_trait_data to get trait_data
trait_data = subset(dd_trait_data, (Day == 1 & EventNum == 1 & Valence == 'Pos'))
```


```{r echo=FALSE, warning=FALSE}
library(lme4) 
```


### Regression analysis for event qualities (EmoRating & Cat), predicting whether student seeks help.
Students are most likely to disclose academic stressors to their peers. They are least likely to disclose financial stressors, although this category was not a significant predictor. Students are slightly less likely than chance to disclose social and work-related stressors — these categories were significant predictors. Students are also more likely to disclose stressors with higher emotion ratings, unless the stressor is work-related.

```{r}
ev_qual_got_help_model = glmer(GotHelp ~ EmoRating_neg_pz*Cat_Soc_Rel + EmoRating_neg_pz*Cat_Health + EmoRating_neg_pz*Cat_Fin + EmoRating_neg_pz*Cat_Job + EmoRating_neg_pz*Cat_Other + (1 | ID) + (0 + EmoRating_neg_pz:Cat_Fin | ID/Dorm) + (0 + Cat_Other | Day), data=subset(dd_trait_data, (Val_EC==-1)), family=binomial, control=glmerControl(optimizer='bobyqa'))

summary(ev_qual_got_help_model)

```


### Regression analysis for trait lonliness and EmoRating, predicting whether student seeks help.
Students who experience more loneliness are less likely than their peers to disclose stressful events. Loneliness remains a significant predictor of disclosure even when controlling for theh objective number of close friends a student has in their dorm. Having more close friends in their dorm does slightly increase the likelihood that a student will disclose a stressor.

```{r}
loneliness_got_help_model = glmer(GotHelp ~ EmoRating_neg_pz*Loneliness_avg_ctr + CloseFrd_Total_ctr*Loneliness_avg_ctr + (1 | ID/Dorm)  + (0 + EmoRating_neg_pz | ID/Dorm), data=subset(dd_trait_data, (Val_EC==-1)), family=binomial, control=glmerControl(optimizer='bobyqa'))

summary(loneliness_got_help_model)

```


### Correlations between loneliness, number of nominations, and "vulnerability ratio."
Each student was given a "vulnerability ratio," calculated by dividing the number of dorm-mates a student nominates as "providing support during difficult times" by the total number of dorm-mates a student nominates as "close friends." Although this "vulnerability ratio" does not correlate with loneliness, the individual nomination totals do. Unsurprisingly, students who nominate more dorm-mates as "close friends" report experiencing slightly less loneliness, as do students who nominate more dorm-mates as "providing support during difficult times". These two nomination totals are moderately positiviely correlated across students.
```{r}


cor.test(trait_data$Loneliness_avg, trait_data$Vulnerability_Ratio) 

cor.test(trait_data$Loneliness_avg, trait_data$CloseFrd_Total)

cor.test(trait_data$Loneliness_avg, trait_data$NegEmoSupp_Total)

cor.test(trait_data$CloseFrd_Total, trait_data$NegEmoSupp_Total)

```


### Regression analysis for trait anxiety and EmoRating, predicting whether student seeks help.
Anxiety is not a significant predictor of self-disclosure.
```{r}
anxiety_got_help_model = glmer(GotHelp ~ EmoRating_neg_pz*STAI_MEAN_ctr + (1 | ID/Dorm)  + (0 + EmoRating_neg_pz | ID), data=subset(dd_trait_data, (Val_EC==-1)), family=binomial, control=glmerControl(optimizer='bobyqa'))

summary(anxiety_got_help_model)

```

### Correlation between anxiety and loneliness.
Anxiety and loneliness are moderately positively correlated.
```{r}
cor.test(trait_data$Loneliness_avg, trait_data$STAI_MEAN)

```


### Regression analysis for trait depression and EmoRating, predicting whether student seeks help.
Depression is not a significant predictor of self-disclosure.
```{r}
depression_got_help_model = glmer(GotHelp ~ EmoRating_neg_pz*CESD_avg_ctr + (1 | ID/Dorm), data=subset(dd_trait_data, (Val_EC==-1)), family=binomial, control=glmerControl(optimizer='bobyqa'))

summary(depression_got_help_model)

```

### Correlation between depression and loneliness.
Depression and loneliness are strongly positively correlated.
```{r}
cor.test(trait_data$Loneliness_avg, trait_data$CESD_avg)

```


### Regression analysis for perceived stress and EmoRating, predicting whether student seeks help.
Perceived stress is not a significant predictor of self-disclosure.
```{r}
stress_got_help_model = glmer(GotHelp ~ EmoRating_neg_pz*PSS_avg_ctr + (1 | ID/Dorm) + (0 + EmoRating_neg_pz | ID/Dorm), data=subset(dd_trait_data, (Val_EC==-1)), family=binomial, control=glmerControl(optimizer='bobyqa'))

summary(stress_got_help_model)

```

### Correlation between perceived stress and loneliness.
Perceived stress and loneliness are moderately positively correlated.
```{r}
cor.test(trait_data$Loneliness_avg, trait_data$PSS_avg)

```


## Next Steps
1) How do students who experience more loneliness feel after disclosing events?
  a) Compared to students who experience less loneliness?
2) Look at how loneliness relates to IRQ-T and IRQ-E
  a) If IRQ-E is lower for lonely students, could there be a self-fulfilling mindset?
3) How do lonely students think others feel after they disclose to them?
  a) If worse than less lonely students, could this be a potential impedence to disclosure?


```{r, echo=FALSE}
#1) Figure out how to predict continuous DV (linear regression?) for NumDrmTld
  #a) test TOIs on NumDrmTld
#2) What's the emotion rating associated with each event category?
#3) **Do students high in lonliness feel better after disclosing events?
  #a) Compared to students who feel less lonlely?
  #b) **How do lonely students fare at the end of the quarter?
```

